### 2024-04-04 scripts/01-download_data.qmd
update

# Read the JSON data from GitHub into R
json_data <- fromJSON(github_url)
```

```{r}
#### Save measurements json data ####
# Code referenced from: chat.openai.com
json_string <- toJSON(json_data, pretty = TRUE)

# Specify the file path
file_path <- here::here("data/raw_data/raw_data.json")

>>>>

# Read the JSON data from GitHub into R
pocket_area_data <- fromJSON(github_url)
```

```{r}
#### Save measurements json data ####
# Code referenced from: chat.openai.com
json_string <- toJSON(pocket_area_data, pretty = TRUE)

# Specify the file path
file_path <- here::here("data/raw_data/pocket_area_data.json")

### 2024-04-04 scripts/02-data_cleaning.qmd
update

#### Preamble ####
# Purpose: Clean the data from from the Womens´s Pockets are Inferior paper by Jan Diehm & Amber Thomas.  
# Author: Hari Lee Robledo
# Date: April 2 2023 
# Contact: hari.leerobledo@mail.utoronto.ca 
# License: MIT
# Pre-requisites: 01-download_data.qmd

@@

# Clean json file (pocket area measurments)
json_file <- here::here("data/raw_data/raw_data.json")

# Read the JSON data from the file
json_data <- fromJSON(json_file)

# Change the name of the raw data into the clean data
cleaned_json_data <-
  clean_names(json_data)

# Select the rows of interest
cleaned_json_data <-
  cleaned_json_data |>
  select(
    updated_style,
    group,
    price_group,
    pocket_area
  )

cleaned_json_data 
```

@@

# save json cleaned data

>>>>

#### Preamble ####
# Purpose: Clean the data from from the Womens´s Pockets are Inferior paper by Jan Diehm & Amber Thomas.  
# Author: Hari Lee Robledo
# Date: April 2 2023 
# Contact: hari.leerobledo@mail.utoronto.ca 
# License: MIT
# Pre-requisites: 01-download_data.R

@@

# Code referenced from: chat.openai.com

# Clean json file (pocket area measurements)
json_file <- here::here("data/raw_data/pocket_area_data.json")

# Read the JSON data from the file
pocket_area_data <- fromJSON(json_file)

# Change the name of the raw data into the clean data
cleaned_pocket_area_data <-
  clean_names(pocket_area_data)

# Select the rows of interest
cleaned_pocket_area_data <-
  cleaned_pocket_area_data |>
  select(
    updated_style,
    group,
    price_group,
    pocket_area
  )

cleaned_pocket_area_data
```

@@

# save json cleaned data (pocket area measurements)
